### 2019-09-25 reports/thesis/book.tex
Revise

\documentclass[12pt, a4paper, oneside]{memoir}
%oneside for soft copy
%twoside for hard final copy
\setlrmargins{4cm}{*}{*}
\checkandfixthelayout
%\documentclass[12pt, a4paper, oldfontcommands]{memoir}
%\documentclass[12pt, a4paper]{report}

@@

The uncertainty of the projection was modelled using a compound Poisson distribution. This arises from x-ray photon arrivals being a Poisson process and each photon has random energy. This results in a linear relationship between the mean and variance of the grey value in the projection. Fitting of the compound Poisson distribution using the expectation-maximisation algorithm was unsuccessful due to identifiability issues with the model. Instead, a gamma-distributed generalised linear model was fitted and used for variance prediction to quantify the uncertainty.

@@

\chapter{Conclusion}
\label{chapter6}
To summarise the thesis, Figure \ref{fig:evaluation_flowchart} shows a flowchart of the process of the experiment. A test sample was designed using a CAD model and was manufactured with purposefully designed voids. Replicate x-ray projections were taken of the test sample with voids as well as a simulation of that projection without the voids using \emph{aRTist}. The obtained projections were used to help align the simulated projection. The experiment aimed to develop a statistical method to detect the designed voids.

\begin{figure}
  \centering
  \includegraphics[width=0.65\textwidth]{../figures/flowchart.pdf}
  \caption{Flowchart showing the process of obtaining and comparing a projection of the test sample with the simulated projection. This results in pixels being highlighted as positive for defects.}
  \label{fig:evaluation_flowchart}
\end{figure}

@@

In Chapter \ref{chapter5}, the replicated projections were split into two. 19 randomly selected projections were used for the variance-mean model to fit onto. The remaining projection was compared with the simulated projection in the face of uncertainty. The uncertainty was predicted using the variance-mean model. Hypothesis testing was done on the test statistics, one for each pixel in a projection. Unfortunately, the simulation was not perfect which led to model misspecification, thus, false positives. The empirical null filter was developed and used to smooth the test statistics. This allows the hypotheses test to pick out areas which are unusual and unlike its neighbours. The filtered test statistics were converted to $p$-values so that hypotheses testing can be done to detect the voids.

Two angular projections were looked at in this thesis. The angles were selected by the engineers, in calibration with this experiment, so that all of the voids were visible in a single projection. Defect detection can be tough if a difficult projection angle was used. Perhaps this method could be extended by analysing more angular projections independently to pick up voids which may be hidden at a particular projection angle. Another possible extension is to integrate \emph{aRTist} into the inference. for example, the simulated projection could be realigned to minimise the number of positives. This will help eliminate sources of error due to \emph{aRTist}. A problem with this suggestion is that aligning the simulated projection is a high dimensional problem \citep{brierley2018optimized}.

In the ABS test sample, voids in the order of millimetres were detectable using this method. Further work could include test samples made from materials such as titanium alloys (Ti-6Al-4V). This can be challenging because artefacts, such as streaks, can appear when using XCT for metal parts \citep{deman1998metal, nawaz2014metal}. Another problem is that because titanium products are created using a power-based method, powder may become trapped \citep{brierley2018optimized} in designed voids. This results in voids appearing with less contrast in the projections, making it harder to detect.

This thesis is a contribution to real-time quality control for additive manufacturing. A powerful multi-core computer could be used to conduct the statistical analysis on a few x-ray projections of AM products on a conveyor belt. By using fewer projections, quality control can be faster which advances the development and increases the scope of applications of additive manufacturing.

>>>>

\documentclass[12pt, a4paper, oneside]{memoir}
%oneside for soft copy
%twoside for hard final copy
\setlrmargins{4.3cm}{*}{*}
\checkandfixthelayout
%\documentclass[12pt, a4paper, oldfontcommands]{memoir}
%\documentclass[12pt, a4paper]{report}

@@

The uncertainty of the projection was modelled using a compound Poisson distribution. This arises from x-ray photon arrivals being a Poisson process and each photon has random energy. This results in a linear relationship between the mean and variance of the grey values in the projection. Fitting of the compound Poisson distribution using the expectation-maximisation algorithm was unsuccessful due to identifiability issues with the model. Instead, a gamma-distributed generalised linear model was fitted onto sample variance-mean data and used for variance prediction to quantify the uncertainty.

@@

\chapter{Conclusion}
\label{chapter6}
To summarise the thesis, Figure \ref{fig:evaluation_flowchart} shows a flowchart of the process of the experiment. An ABS test sample, with purposefully designed voids, was created using a CAD model and manufactured using fused deposition modelling. Replicate x-ray projections were taken of the test sample with voids as well as a simulation of that projection without the voids using \emph{aRTist}. The obtained projections were used to help align the simulated projection. The experiment aimed to develop a statistical method to detect the designed voids.

\begin{figure}
  \centering
  \includegraphics[width=0.64\textwidth]{../figures/flowchart.pdf}
  \caption{Flowchart showing the process of obtaining and comparing a projection of the test sample with the simulated projection. This results in pixels being highlighted as positive for defects.}
  \label{fig:evaluation_flowchart}
\end{figure}

@@

In Chapter \ref{chapter5}, the replicated projections were split into two. 19 randomly selected projections were used for the variance-mean model to fit onto. The remaining projection was compared with the simulated projection in the face of uncertainty. The uncertainty was predicted using the variance-mean model. Hypotheses testing was done on the test statistics, one for each pixel in a projection. Unfortunately, the simulation was not perfect which led to model misspecification, thus, false positives. The empirical null filter was developed and used to smooth the test statistics. This allows the hypotheses test to pick out areas which are unusual and unlike its neighbours. The filtered test statistics were converted to $p$-values so that hypotheses testing can be done to detect the voids.

Two angular projections were looked at in this thesis. The angles were selected by the engineers, in calibration with this experiment, so that all of the voids were visible in a single projection. Defect detection can be tough if a difficult projection angle was used. Perhaps this method could be extended by analysing more angular projections independently to pick up voids which may be hidden at a particular projection angle. Another possible extension is to integrate \emph{aRTist} into the inference, for example, the simulated projection could be realigned to minimise the number of positives. This will help eliminate sources of error due to \emph{aRTist}. A problem with this suggestion is that aligning the simulated projection is a high dimensional problem \citep{brierley2018optimized}.

Voids in the order of millimetres were detectable using this method. Further work could include test samples made from materials such as titanium alloys (Ti-6Al-4V). This can be challenging because artefacts, such as streaks, can appear when using XCT for metal parts \citep{deman1998metal, nawaz2014metal}. Another problem is that because titanium products are created using a power-based method, powder may become trapped \citep{brierley2018optimized} in designed voids. This results in voids appearing with less contrast in the projections, making it harder to detect.

This thesis is a contribution to real-time quality control for AM. A powerful multi-core computer could be used to conduct the statistical analysis on a few x-ray projections of AM products on a conveyor belt. By using fewer projections, quality control can be faster which advances the development, and increases the scope of applications, of AM.

### 2019-09-25 reports/thesis/chapters/1_literatureReview.tex
Revise

Fused deposition modelling is another liquid-based AM technology. A jetting head, or nozzle, deposit the molten material onto a platform or on top of the previous layer. The material is usually plastic in the form of a thin filament. It is heated to just above its melting points, typically \SI{1}{\degreeCelsius} \citep{crump1992apparatus}, so that it cools down within \SI{0.1}{\second} \citep{kruth1991material}. The platform moves, and controlled by a computer, in the $xy$ plane, or left to right and front to back, to produce a layer. The jetting head can move in the $z$-axis, or up and down, to manufacture the next layer. In the original patent by \cite{crump1992apparatus}, the thickness can be as thin as 0.000\,1 inches (\SI{0.003}{\milli\metre}).

@@

In manufacturing and metrology, high power x-rays can be used in XCT because there is no consequence of the manufactured object absorbing the radiation. As a result, the XCT setup is different. The object is held by foam on a turntable and placed between an x-ray source and an x-ray detector. X-ray projections are taken while the object rotates. Typically the x-ray is a cone-beam \citep{kruth2011computed}. This is illustrated in Figure \ref{fig:literature_xct}.

@@

The electrons can interact with the anode in many ways. The electrons can be deflected or decelerated due to the electric field from the nucleus of the target anode material. The energy lost by the electrons is emitted as bremsstrahlung radiation. The energy of the radiation depends on the potential difference in the x-ray tube, as this determines the energy of the fired electrons, and also the proton number of the anode target because this affects the electric field produced by the nucleus in the anode target \citep{sun2012overview}. Another interaction is when the electrons may collide with the nucleus in the anode target, exciting an inner shell electron and ionizing it. This produces a vacancy in the electron shell and emits a photon when the excited electron drops down back to the ground state. This is known as characteristic radiation and the energy emitted is discrete and depends on the material in the anode target \citep{sun2012overview}.

@@

The scanned object is exposed to x-ray photons which undergo attenuation when interacting with the object in several ways \citep{cantatore2011introduction}. The object can absorb the photons via the photoelectric effect. In the photoelectric effect, a photon transfer all of its energy to a bounded electron and ejects it from the atom in the object \citep{millikan1916direct}. Photons can be scattered by the object by colliding inelastically with and transfers its energy to an electron. This process is known as Compton scattering \citep{compton1923quantum}. The photoelectric effect and Compton scattering cause several photons to be undetectable. If some of the photons avoid these processes, they are detected and their energy is left unaffected.

Beer's law simplifies these quantum mechanistic process. Suppose the x-ray beam with a rate of emission $I_0$ is mono-energetic and travels in a straight line in the $x$-axis. Let $\mu(x)$ be the attenuation coefficient of the object and the x-ray beam has a rate of emission $I$ after attenuation. A differential equation can be set up to model the decay of photons as it attenuates through the object such that
\begin{equation}
\dfrac{\diff I}{\diff x} = -I\mu(x)
\end{equation}
which can be solved
\begin{equation}
I = I_0\exp\left[\int_{x \in \text{path of photon}}-\mu(x)\diff x\right] \ .
\label{eq:beerLaw}
\end{equation}
However, the photoelectric effect and Compton scattering, thus the attenuation coefficient as well, depends on the energy of the photons \citep{elbakri2002statistical}. Therefore $\mu(x,E)$ should be made dependent on the energy of the photons \citep{cantatore2011introduction} and can cause some inaccuracies in Beer's law. In general low energy photons are more likely to be absorbed and scattered than high energy photons, which increases the average energy of the detected photons \citep{sun2012overview}. This is called beam hardening.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{../figures/literatureReview/literature_magnification.png}
  \caption{The magnification can be adjusted by adjusting the distances between the x-ray source, the object and the x-ray detector. Because of a finite x-ray spot size, blurry effects are produced using a magnification too large. Reprinted from \cite{kruth2011computed}\textsuperscript{\textcopyright} with permission from Elsevier.}
  \label{fig:literature_magnification}
\end{figure}

>>>>

Fused deposition modelling is another liquid-based AM technology. A jetting head, or nozzle, deposit the molten material onto a platform or on top of the previous layer. The material is usually plastic in the form of a thin filament. It is heated to just above its melting points, typically \SI{1}{\degreeCelsius} \citep{crump1992apparatus}, so that it cools down within \SI{0.1}{\second} \citep{kruth1991material}. The platform moves, and controlled by a computer, in the $xy$-plane, or left to right and front to back, to produce a layer. The jetting head can move in the $z$-axis, or up and down, to manufacture the next layer. In the original patent by \cite{crump1992apparatus}, the thickness can be as thin as 0.000\,1 inches (\SI{0.003}{\milli\metre}).

@@

In manufacturing and metrology, high power x-rays can be used in XCT because there is no consequence of the manufactured object absorbing the radiation. As a result, the XCT setup is different. The object is held by foam on a turntable and placed between an x-ray source and an x-ray detector. X-ray projections are taken while the object rotates. Typically, the x-ray is a cone-beam \citep{kruth2011computed}. This is illustrated in Figure \ref{fig:literature_xct}.

@@

The electrons can interact with the anode in many ways. The electrons can be deflected or decelerated due to the electric field from the nucleus of the target anode material. The energy lost by the electrons is emitted as bremsstrahlung radiation. The energy of the radiation depends on the potential difference in the x-ray tube, as this determines the energy of the fired electrons, and also the proton number of the anode target because this affects the electric field produced by the nucleus in the anode target \citep{sun2012overview}. Another interaction is when the electrons may collide with the nucleus in the anode target, exciting an inner shell electron and ionising it. This produces a vacancy in the electron shell and emits a photon when the excited electron drops down back to the ground state. This is known as characteristic radiation and the energy emitted is discrete and depends on the material in the anode target \citep{sun2012overview}.

@@

The scanned object is exposed to x-ray photons which undergo attenuation when interacting with the object in several ways \citep{cantatore2011introduction}. The object can absorb the photons via the photoelectric effect. In the photoelectric effect, a photon transfer all of its energy to a bounded electron and ejects it from the atom in the object \citep{millikan1916direct}. Photons can be scattered by the object by colliding inelastically with and transfers its energy to an electron. This process is known as Compton scattering \citep{compton1923quantum}. The photoelectric effect and Compton scattering cause several photons to be undetectable. If some of the photons avoid these processes, they are detected with their energy unaffected.

Beer's law simplifies these quantum mechanistic process. Suppose the x-ray beam with a rate of emission $I_0$ is mono-energetic and travels in a straight line in the $x$-axis. Let $\mu(x)$ be the attenuation coefficient of the object and the x-ray beam has a rate of emission $I$ after attenuation. A differential equation can be set up to model the decay of photons as it attenuates through the object such that
\begin{equation}
\dfrac{\diff I}{\diff x} = -I\mu(x)
\end{equation}
which can be solved
\begin{equation}
I = I_0\exp\left[\int_{x \in \text{path of photon}}-\mu(x)\diff x\right] \ .
\label{eq:beerLaw}
\end{equation}
However, the photoelectric effect and Compton scattering, thus the attenuation coefficient as well, depends on the energy of the photons \citep{elbakri2002statistical}. Therefore $\mu(x,E)$ should be made dependent on the energy of the photons \citep{cantatore2011introduction} and can cause some inaccuracies in Beer's law. In general, low energy photons are more likely to be absorbed and scattered than high energy photons, which increases the average energy of the detected photons \citep{sun2012overview}. This is called beam hardening.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{../figures/literatureReview/literature_magnification.png}
  \caption{The magnification can be tuned by adjusting the distances between the x-ray source, the object and the x-ray detector. Because of a finite x-ray spot size, blurry effects are produced using a magnification too large. Reprinted from \cite{kruth2011computed}\textsuperscript{\textcopyright} with permission from Elsevier.}
  \label{fig:literature_magnification}
\end{figure}

### 2019-09-25 reports/thesis/chapters/2_dataCollection.tex
Revise

The test object is a cuboid (\SI{40.0}{\milli\metre} $\times$ \SI{40.0}{\milli\metre} $\times$ \SI{60.0}{\milli\metre}) with voids. The voids were of diameters \SI{2.4}{\milli\metre}, \SI{1.2}{\milli\metre}, \SI{0.6}{\milli\metre} and \SI{0.3}{\milli\metre}. 6 voids for each diameter were designed in the CAD. Voids with diameters \SI{2.4}{\milli\metre} and \SI{0.6}{\milli\metre} were regularly arranged, the other ones were arranged irregularly. The CAD model of the test sample is shown in Figure \ref{fig:inference_testObject}.

@@

Two datasets were collected and named \texttt{AbsNoFilter} and \texttt{AbsFilter}. They contain replicate projections of the test sample at two different angles, named $\ang{30}$ and $\ang{120}$, as well as replicate greyscale projections. To investigate the effects of beam hardening, no x-ray filter was used in \texttt{AbsNoFilter}, a filter was used in \texttt{AbsFilter}.

@@

\begin{sidewaystable}
\centering
\begin{tabular}{l|ll}
                                                       & \multicolumn{2}{c}{Dataset name}                      \\
                                                       & \texttt{AbsNoFilter} & \texttt{AbsFilter}             \\ \hline
potential difference (\SI{}{\kilo\volt})               & 80                   & 80                             \\
power (\SI{}{\watt})                                   & 36                   & 20                             \\
filter                                                 & no filter            & \SI{0.35}{\milli\metre} copper \\
time exposure (\SI{}{\milli\second})                   & 708                  & 500                            \\
distance from source to object (\SI{}{\milli\metre})   & 217                  & 168                            \\
distance from source to detector (\SI{}{\milli\metre}) & 1178                 & 876                            \\
number of replications for each angle                  & 100                  & 20                             \\ \hline
powers used for greyscale projections (\SI{}{\watt})   & 0.0                  & 0.0                            \\
\multicolumn{1}{c|}{\vdots}                            & 10                   & 5.0                            \\
\multicolumn{1}{c|}{\vdots}                            & 18                   & 10                             \\
\multicolumn{1}{c|}{\vdots}                            & 28                   & 15                             \\
\multicolumn{1}{c|}{\vdots}                            & 36                   & 20                             \\
number of replications for each power                  & 20                   & 20                             
\end{tabular}
\caption{Properties of the three datasets obtained for the experiment.}
\label{table:data_dataset}
\end{sidewaystable}

@@

The projections show the test sample, but, with panel and spot effects. The structure of the 32 panels are predominate in the black image, in particular, this was observed by \cite{yang2009evaluation} as well. This is concerning because systematic errors could be introduced as a result of the panel effects in the black image. This should not happen because, in a black image, the detector is exposed only to background radiation. The x-ray spot can be observed, in particular, in the white image, and this is the result of using a cone beam.

@@

Let $S_{x,y}(P)$ be the greyscale projection when exposed to x-rays produced by an x-ray tube with power $P$ for some fixed time exposure $\tau$. $S_{x,y}(P)$ may be averaged over replications. Let $x=1,2,3,\dotsc, W$ and $y=1,2,3,\dotsc,H$. Let $N_{x,y}$ be the obtained projection of the test sample when exposed to x-rays produced by an x-ray tube with power $P_\text{proj}$ for some fixed time exposure $\tau$. The black and white image can be expressed as $\text{black}_{x,y}=S_{x,y}(0)$ and $\text{white}_{x,y}=S_{x,y}(P_\text{proj})$ respectively. For both the greyscale projections and the projection of the test sample, the power was varied by fixing the potential difference and varying the current of the x-ray tube.

@@

\begin{figure}
  \centering
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_interpolation.eps}
      \caption{Linear regression}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_gradient_linear.eps}
      \caption{$b_{x,y}$}
    \end{subfigure}
  }
  \caption{For each pixel, a linear regression was fitted on the within projection mean versus the grey value for each greyscale projection. The \texttt{AbsNoFilter} dataset was used. 3 random pixels were used to illustrate this in a). b) shows the fitted gradient for all pixels.}
  \label{fig:data_shadingCorrectionExample_gainMap}
\end{figure}

@@

\begin{figure}
  \centerline{
    \begin{subfigure}[b]{\textwidth}
      \includegraphics[width=\subSize]{../figures/data/oddEvenPlot1_null.eps}
      \includegraphics[width=\subSize]{../figures/data/oddEvenPlot2_null.eps}
      \caption{No shading correction}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\textwidth}
      \includegraphics[width=\subSize]{../figures/data/oddEvenPlot1_bw.eps}
      \includegraphics[width=\subSize]{../figures/data/oddEvenPlot2_bw.eps}
      \caption{BW shading correction}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\textwidth}
      \includegraphics[width=\subSize]{../figures/data/oddEvenPlot1_linear.eps}
      \includegraphics[width=\subSize]{../figures/data/oddEvenPlot2_linear.eps}
      \caption{linear shading correction}
    \end{subfigure}
  }
  \caption{Left shows the profile plot of a \texttt{AbsNoFilter} black image at $(879,y)$ using various shading corrections. Right shows two curves for odd and even $y$.}
  \label{fig:data_oddEven}
\end{figure}

>>>>

The test object is a cuboid (\SI{40.0}{\milli\metre} $\times$ \SI{40.0}{\milli\metre} $\times$ \SI{60.0}{\milli\metre}) with voids. The voids were of diameters \SI{2.4}{\milli\metre}, \SI{1.2}{\milli\metre}, \SI{0.6}{\milli\metre} and \SI{0.3}{\milli\metre}. 6 voids for each diameter were designed in the CAD model. Voids with diameters \SI{2.4}{\milli\metre} and \SI{0.6}{\milli\metre} were regularly arranged, the other ones were arranged irregularly. The CAD model of the test sample is shown in Figure \ref{fig:inference_testObject}.

@@

Two datasets were collected and named \texttt{AbsNoFilter} and \texttt{AbsFilter}. They contain replicate projections of the test sample at two different angles, named $\ang{30}$ and $\ang{120}$, as well as replicate greyscale projections. To investigate the effects of beam hardening, no x-ray filter was used in \texttt{AbsNoFilter} and a filter was used in \texttt{AbsFilter}.

@@

\begin{sidewaystable}
\centering
\begin{tabular}{l|cc}
                                                       & \multicolumn{2}{c}{Dataset name}                      \\
                                                       & \texttt{AbsNoFilter} & \texttt{AbsFilter}             \\ \hline
potential difference (\SI{}{\kilo\volt})               & 80                   & 80                             \\
power (\SI{}{\watt})                                   & 36                   & 20                             \\
filter                                                 & no filter            & \SI{0.35}{\milli\metre} copper \\
time exposure (\SI{}{\milli\second})                   & 708                  & 500                            \\
distance from source to object (\SI{}{\milli\metre})   & 217                  & 168                            \\
distance from source to detector (\SI{}{\milli\metre}) & 1178                 & 876                            \\
number of replications for each angle                  & 100                  & 20                             \\ \hline
powers used for greyscale projections (\SI{}{\watt})   & 0.0                  & 0.0                            \\
\multicolumn{1}{c|}{\vdots}                            & 10                   & 5.0                            \\
\multicolumn{1}{c|}{\vdots}                            & 18                   & 10                             \\
\multicolumn{1}{c|}{\vdots}                            & 28                   & 15                             \\
\multicolumn{1}{c|}{\vdots}                            & 36                   & 20                             \\
number of replications for each power                  & 20                   & 20                             
\end{tabular}
\caption{Properties of the two datasets obtained for the experiment.}
\label{table:data_dataset}
\end{sidewaystable}

@@

The projections show the test sample, but, with panel and spot effects. The structure of the 32 panels are predominate in the black image, in particular, this was observed by \cite{yang2009evaluation} as well. This is concerning because systematic errors could be introduced as a result of the panel effects in the black image. A black image should be flat because the detector is exposed only to background radiation. The x-ray spot can be observed, in particular, in the white image, and this is the result of using a cone beam.

@@

Let $S_{x,y}(P)$ be the greyscale projection when exposed to x-rays produced by an x-ray tube with power $P$ for some fixed time exposure $\tau$. $S_{x,y}(P)$ may be averaged over replications. Let $x=1,2,3,\dotsc, W$ and $y=1,2,3,\dotsc,H$. Let $N_{x,y}$ be the obtained projection of the test sample when exposed to x-rays produced by an x-ray tube with power $P_\text{proj}$ for some fixed time exposure $\tau$. The black and white image can be expressed as $\text{black}_{x,y}=S_{x,y}(0)$ and $\text{white}_{x,y}=S_{x,y}(P_\text{proj})$ respectively. The power was varied by fixing the potential difference and varying the current of the x-ray tube.

@@

\begin{figure}
  \centering
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_interpolation.eps}
      \caption{Linear regression}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_gradient_linear.eps}
      \caption{$b_{x,y}$}
    \end{subfigure}
  }
  \caption{For each pixel, a linear regression was fitted on the within projection mean versus the pixel's grey value. The \texttt{AbsNoFilter} dataset was used. 3 random pixels were used to illustrate this in a). b) shows the fitted gradient for all pixels.}
  \label{fig:data_shadingCorrectionExample_gainMap}
\end{figure}

@@

\begin{figure}
  \centerline{
    \begin{subfigure}[b]{\textwidth}
      \includegraphics[width=\subSize]{../figures/data/oddEvenPlot1_null.eps}
      \includegraphics[width=\subSize]{../figures/data/oddEvenPlot2_null.eps}
      \caption{No shading correction}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\textwidth}
      \includegraphics[width=\subSize]{../figures/data/oddEvenPlot1_bw.eps}
      \includegraphics[width=\subSize]{../figures/data/oddEvenPlot2_bw.eps}
      \caption{BW shading correction}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\textwidth}
      \includegraphics[width=\subSize]{../figures/data/oddEvenPlot1_linear.eps}
      \includegraphics[width=\subSize]{../figures/data/oddEvenPlot2_linear.eps}
      \caption{linear shading correction}
    \end{subfigure}
  }
  \caption{Left shows the profile plot of an \texttt{AbsNoFilter} black image at $(879,y)$ using various shading corrections. Right shows two curves for odd and even $y$.}
  \label{fig:data_oddEven}
\end{figure}
